---
title: "Birds Observed Richness"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(lmerTest)
library(lme4)
library(effects)
library(MuMIn)
library(DHARMa)
library(glmmTMB)
library(performance)
library(sjPlot)
library(patchwork)
library(ggeffects)
```

```{r Import Data, include=FALSE}
CD <- read_csv("Data/NEW_BirdRichness.csv")
covs <- read_csv("Data/Cameras_ALL_Covs.csv")
```

```{r Join covariates DF to richness DF, include=FALSE}
covs <- covs %>% 
  mutate(Camera = paste(Site, Camera, sep = "_")) %>% 
  select(Site, Camera)

CD <- left_join(CD, covs)
```



## INITIAL MODELS

```{r Moon phase variable comparison}
mm1 <- glmmTMB(rich ~ scale(M_Illum) + (1|Cluster/Site), data = CD, family = compois)
mm2 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

AICc(mm1, mm2)

summary(mm2)
```

mIndex model has lower AICc score & p-value < 0.15 -> include in global model



```{r Landcover and Julian date model}
lm2 <- glmmTMB(rich ~ Landcover + scale(JDay) + (1|Cluster/Site), data = CD, family = compois)

summary(lm2)
```

Both LC and JDay had p-values > 0.15 -> neither included in global model



## Global Models


```{r Treatment global model}
Tgm1 <- glmmTMB(rich ~ Treatment * scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
```

```{r Dredge Treatment global model}
options(na.action = "na.fail")
GD1 <- dredge(Tgm1)
options(na.action = "na.omit")
GD1
```

Top-ranked models from dredge (delta AICc <= 2):

  cnd((Int)) dsp((Int)) cnd(scl(mIn)) cnd(Trt) cnd(scl(mIn):Trt) df   logLik  AICc delta weight
3     -1.756          +                      +                    7 -102.685 219.9  0.00  0.291
4     -1.752          +       -0.3393        +                    8 -101.634 219.9  0.04  0.285
2     -2.032          +       -0.3483                             5 -105.169 220.6  0.73  0.202
1     -2.031          +                                           4 -106.238 220.7  0.78  0.197



```{r Treatment models top-ranked set}
Tfm1 <- glmmTMB(rich ~ Treatment + (1|Cluster/Site), data = CD, family = compois)

Tfm2 <- glmmTMB(rich ~ scale(mIndex) + Treatment + (1|Cluster/Site), data = CD, family = compois)

Tfm3 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

Nullm

summary(Tfm1)
```

```{r}
TukeyHSD(Tfm1)
confint(Tfm1, method = "Wald")
```





```{r Numerical variables global model}
# Compare LAeq and LZeq models

Ngm1 <- glmmTMB(rich ~ scale(Laeq) * scale(mIndex) + 
                       scale(Laeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

Ngm2 <- glmmTMB(rich ~ scale(Lzeq) * scale(mIndex) + 
                       scale(Lzeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

AICc(Ngm1, Ngm2)
```

Laeq model very slightly better (delta AICc ~ 0.2)


```{r Dredge Laeq global model}
options(na.action = "na.fail")
GD2 <- dredge(Ngm1)
options(na.action = "na.omit")
GD2
```


   Model          Delta   AICc
5  Moon           0.00    220.6        
1  Null model     0.05    220.7  
7  Lux + Moon     1.91    222.5
3  Lux            1.98    222.6


Only model from Lux/LAeq dredge that's competitive is Moon only model which is already in Treatment model set
For final results, just go with the top-ranked models from Treatment dredge



```{r Model Summary Plot}
BirdSppPlot <- plot_models(Tfm1, Tfm2, Tfm3,
            vline.color = "black",
show.legend = FALSE,
transform = NULL,
std.est="std2",
spacing=.5,
ci.lvl=0.95,
grid.breaks = 1,
axis.labels=c("Moon Index", "Treatment: Combined", "Treatment: Light", "Treatment: Noise"),
axis.title = "Effect Size",
colors=c("royalblue1", "coral1", "turquoise3"),
p.shape = TRUE) + 
#  ylim(-0.5, 1) +
  theme_classic(base_size = 18) +
  ggtitle("Bird Observed Richness") +
  theme(plot.title = element_text(size = 12, face = "bold"))

BirdSppPlot
```





