---
title: "Mammal Species Observed Richness"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(lmerTest)
library(lme4)
library(effects)
library(MuMIn)
library(DHARMa)
library(glmmTMB)
library(performance)
library(sjPlot)
library(patchwork)
library(ggeffects)
```

```{r Import Data, include=FALSE}
CD <- read_csv("Data/NEW_MammalRichness.csv")
covs <- read_csv("Data/Cameras_ALL_Covs.csv")
```

```{r Join covariates DF to richness DF, include=FALSE}
covs <- covs %>% 
  mutate(Camera = paste(Site, Camera, sep = "_")) %>% 
  select(Site, Camera)

CD <- left_join(CD, covs)
```



## INITIAL MODELS

```{r Moon phase variable comparison}
mm1 <- glmmTMB(rich ~ scale(M_Illum) + (1|Cluster/Site), data = CD, family = compois)
mm2 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

AICc(mm1, mm2)

summary(mm2)
```

mIndex model has lower AICc score & p-value < 0.15 -> include in global model



```{r Landcover and Julian date model}
lm2 <- glmmTMB(rich ~ Landcover + scale(JDay) + (1|Cluster/Site), data = CD, family = compois)

summary(lm2)
```

Both LC and JDay had p-values > 0.15 -> neither included in global model



## Global Models


```{r Treatment global model}
Tgm1 <- glmmTMB(rich ~ Treatment * scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
```

```{r Dredge Treatment global model}
options(na.action = "na.fail")
GD1 <- dredge(Tgm1)
options(na.action = "na.omit")
GD1
```

Top-model set from dredge:

  cnd((Int)) dsp((Int)) cnd(scl(mIn)) cnd(Trt) cnd(scl(mIn):Trt) df   logLik  AICc delta weight
2    -0.4149          +       -0.2143                             5 -215.051 440.4  0.00  0.384
4    -0.6804          +       -0.2159        +                    8 -211.899 440.4  0.08  0.368
------------------------------------------------------------------------------------------------
3    -0.6747          +                      +                    7 -214.185 442.9  2.51  0.110
1    -0.4106          +                                           4 -217.407 443.0  2.62  0.103


```{r Treatment models top-ranked set}
Tfm1 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
Tfm2 <- glmmTMB(rich ~ scale(mIndex) + Treatment + (1|Cluster/Site), data = CD, family = compois)
```

```{r}
summary(Tfm2)
```

Summary:
Moon Index - strong effect in both models
Treatment - strong effect in 2nd ranked model




```{r Numerical variables global model}
# Compare LAeq and LZeq models

Ngm1 <- glmmTMB(rich ~ scale(Laeq) * scale(mIndex) + 
                       scale(Laeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

Ngm2 <- glmmTMB(rich ~ scale(Lzeq) * scale(mIndex) + 
                       scale(Lzeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

AICc(Ngm1, Ngm2)
```

Laeq model slightly better (delta AICc ~ 1)


```{r Dredge Laeq global model}
options(na.action = "na.fail")
GD2 <- dredge(Ngm1)
options(na.action = "na.omit")
GD2
```

#      Model               Delta AICc   AICc score               
7   Lux + Moon            0.00            436.9
8   Lux + LAeq + Moon     2.10            439.0
3   Lux                   2.68            439.5
16  Lux*Laeq + Moon       2.82            439.7
5   Moon                  3.50            440.4


**Top-ranked Treatment models competitive w/ top-ranked LAeq/Lux models (at delta 4 AICc level, not delta 2)

```{r}
Nfm1 <- glmmTMB(rich ~ scale(Lux) + 
                       scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

Nfm2 <- glmmTMB(rich ~ scale(Lux) + 
                       scale(mIndex) + 
                       scale(Laeq) + (1|Cluster/Site), data = CD, family = compois)

Nfm3 <- glmmTMB(rich ~ scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

Nfm4 <- glmmTMB(rich ~ scale(Lux)*scale(Laeq) + 
                       scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

Nfm5 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

summary(Nfm1)
```

```{r}
confint(Nfm1, method = "Wald")
```




Include all models (Treatment and Lux/Laeq) that are w/i 2 delta AICc of top-ranked Lux/Laeq model?
Or just go with the top-ranked Lux/LAeq models?

```{r Model Summary Plot}
MammSppPlot <- plot_models(Nfm1,
            vline.color = "black",
show.legend = FALSE,
transform = NULL,
std.est="std2",
spacing=.5,
ci.lvl=0.95,
grid.breaks = 1,
#axis.labels=c("Light (Lux)","Moon Index", "Treatment: Control", "Treatment: Light", "Treatment: Noise"),
axis.title = "Effect Size",
colors=c("royalblue1"),
p.shape = TRUE) + 
  ylim(-0.5, 0.5) +
  theme_classic(base_size = 18) +
  ggtitle("Mammal Observed Richness") +
  theme(plot.title = element_text(size = 12, face = "bold"))

MammSppPlot
```
Triangle = p-value <= 0.01
Closed circle = p-value <= 0.05
Open circle = p-value <= 0.15








