---
title: "All Species Observed Richness"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(lmerTest)
library(lme4)
library(effects)
library(MuMIn)
library(DHARMa)
library(glmmTMB)
library(performance)
library(sjPlot)
library(patchwork)
library(ggeffects)
```

```{r Import Data, include=FALSE}
CD <- read_csv("Data/NEW_AllCamsCounts.csv")
covs <- read_csv("Data/Cameras_ALL_Covs.csv")
```

```{r Join covariates DF to richness DF, include=FALSE}
covs <- covs %>% 
  mutate(Camera = paste(Site, Camera, sep = "_")) %>% 
  select(Site, Camera)

CD <- left_join(CD, covs)
```


Since the way we have the data formatted, continuous variables are averaged over the 3-day period the cameras were out. As such, can only use numerical values for moonlight (Moon_Illum and Moon_Index)


## INITIAL MODELS

```{r Moon phase variable comparison}
mm1 <- glmmTMB(rich ~ scale(M_Illum) + (1|Cluster/Site), data = CD, family = compois)
mm2 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)

AICc(mm1, mm2)

summary(mm2)
```

mIndex model has lower AICc score & p-value < 0.15 -> include in global model



```{r Landcover and Julian date model}
lm2 <- glmmTMB(rich ~ Landcover + scale(JDay) + (1|Cluster/Site), data = CD, family = compois)

summary(lm2)
```

Both LC and JDay had p-values > 0.15 -> neither included in global model



## Global Models


```{r Treatment global model}
Tgm1 <- glmmTMB(rich ~ Treatment * scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
```

```{r Dredge Treatment global model}
options(na.action = "na.fail")
GD1 <- dredge(Tgm1)
options(na.action = "na.omit")
GD1
```

Dredge results tabel:

  cnd((Int)) dsp((Int)) cnd(mIn) cnd(Trt) cnd(mIn:Trt) df   logLik  AICc delta weight
2    0.13090          +  -0.5077                        5 -281.496 573.3  0.00  0.507
1   -0.02168          +                                 4 -282.707 573.6  0.33  0.429
--------------------------------------------------------------------------------------
4    0.09662          +  -0.5096        +               8 -281.073 578.8  5.54  0.032
3   -0.05546          +                 +               7 -282.291 579.1  5.83  0.028
8    0.08592          +  -0.4534        +            + 11 -279.742 582.7  9.44  0.005

```{r}
Tfm1 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
Tfm2 <- glmmTMB(rich ~ (1|Cluster/Site), data = CD, family = compois)
```







```{r Numerical variables global model}
# Compare LAeq and LZeq models

Ngm1 <- glmmTMB(rich ~ scale(Laeq) * scale(mIndex) + 
                       scale(Laeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

Ngm2 <- glmmTMB(rich ~ scale(Lzeq) * scale(mIndex) + 
                       scale(Lzeq) * scale(Lux) + (1|Cluster/Site), data = CD, family = compois)

AICc(Ngm1, Ngm2)
```

Laeq model slightly better but both models essentially equal (delta AICc ~ 0.8)


```{r Dredge Laeq global model}
options(na.action = "na.fail")
GD2 <- dredge(Ngm1)
options(na.action = "na.omit")
GD2
```

Model selection table 
   cnd((Int)) dsp((Int))  cnd(Laq) cnd(Lux)  cnd(mIn) cnd(Laq:Lux) cnd(Laq:mIn) df   logLik  AICc delta 
5    0.130900          +                    -0.507700                            5 -281.496 573.3  0.00
1   -0.021680          +                                                         4 -282.707 573.6  0.33
7    0.152700          +            -0.2687 -0.503400                            6 -281.009 574.4  1.14
3    0.001867          +            -0.2734                                      5 -282.202 574.7  1.41
6   -0.037540          +  0.003743          -0.508800                            6 -281.404 575.2  1.92
--------------------------------------------------------------------------------------------------------
2   -0.164200          +  0.003162                                               5 -282.641 575.6  2.29
16   0.253100          + -0.001867  -5.1470 -0.512100       0.1053               8 -279.701 576.1  2.79
8   -0.003735          +  0.003469  -0.2650 -0.504300                            7 -280.929 576.4  3.10
12   0.118200          + -0.002256  -5.1380                 0.1047               7 -280.942 576.4  3.13
4   -0.128700          +  0.002890  -0.2703                                      6 -282.146 576.7  3.41
22  -0.274700          +  0.009111           0.283800                  -0.01811  7 -281.289 577.1  3.82


```{r}
Nfm1 <- glmmTMB(rich ~ scale(mIndex) + (1|Cluster/Site), data = CD, family = compois)
NullM <- glmmTMB(rich ~ (1|Cluster/Site), data = CD, family = compois)
Nfm2 <- glmmTMB(rich ~ scale(mIndex) + scale(Lux) + (1|Cluster/Site), data = CD, family = compois)
Nfm3 <- glmmTMB(rich ~ scale(Lux) + (1|Cluster/Site), data = CD, family = compois)
Nfm4 <- glmmTMB(rich ~ scale(mIndex) + scale(Laeq) + (1|Cluster/Site), data = CD, family = compois)

summary(Nfm4)
```

```{r}
confint(Nfm4, method = "Wald")
```



Summary:
Moon Index - weak effect in 3/4 top-ranked models
Lux - no effect in any model
Laeq - no effect in any model

**Null model is also highly competitive (2nd ranked, delta AICc = 0.33)


```{r Model Summary Plot for All Species}
AllSppPlot <- plot_models(Nfm1, Nfm2, Nfm3, Nfm4,
            vline.color = "black",
show.legend = FALSE,
transform = NULL,
std.est="std2",
spacing=.5,
ci.lvl=0.95,
grid.breaks = 1,
axis.labels=c("Noise (LAeq)","Light (Lux)","Moon Index"),
axis.title = "Effect Size",
colors=c("royalblue1","coral1","turquoise3","firebrick1"),
p.shape = TRUE) + 
  ylim(-0.4, 0.4) +
  theme_classic(base_size = 18) +
  ggtitle("Total Species Observed Richness") +
  theme(plot.title = element_text(size = 12, face = "bold"))

AllSppPlot
```

