---
title: "Untitled"
author: "JWILLEMS"
date: "3/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, include=FALSE}
library(vegan)
library(multcomp)
library(lme4)
library(performance)
library(MuMIn)
library(blmeco)
library(matrixStats)
library(ecodist)
library(MASS)
options(na.action = "na.fail")
```


```{r}
d <- read.csv("Data/CamTaxaTotal2.csv", header=TRUE)
head(d)
```

```{r}
## how many zeros per treatment
d_zero <- subset(d, d$rich < 1)
d_zero                               # No cameras w/ 0 detections
```


```{r}
# The following indices have binary versions
# use which ever maximizes index. Try gradients of light and noise, but also treatment categories

rankindex(d$Lux, d[2:9],indices = c("euclidean", "manhattan", "gower", "altGower", "canberra", "clark", "kulczynski", "horn", "binomial", "jaccard", "bray"))

# for lux:
# for laeq: 
# for treatment:

betaD1 <-vegdist(d[2:9], method ="horn", binary=FALSE)   # for Treatment model

betD2 <- vegdist(d[2:9], method ="horn", binary=FALSE) 

```


```{r}
#### we can now use a permanova to see whether we see turnover among our treatments

adonis(betaD ~ d$Treatment + d$Laeq + d$Lux + d$Landcover) 



### add pair.wise adonis for treatment conparisons

pairwise.adonis(x=d[,2:9], factor = d$Treatment, sim.function="vegdist", sim.method = "horn", p.adjust.m = "none")
```


Terms added sequentially (first to last)

             Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)   
d$Treatment   3     2.242 0.74721 3.13563 0.05462  0.002 **
d$Laeq        1     0.034 0.03381 0.14189 0.00082  0.930   
d$Lux         1     0.401 0.40054 1.68083 0.00976  0.173   
Residuals   161    38.366 0.23830         0.93480          
Total       166    41.042                 1.00000          


    Pairs             F.Model       R2        p    pADJ
Control vs Light	   1.4788729	0.017505831	0.200	0.200	
Control vs Noise	   4.6567361	0.050806261	0.007	0.007	*
Control vs Combined	 0.5836583	0.007154108	0.623	0.623	
Light vs Noise	     4.4467967	0.051439693	0.015	0.015	.
Light vs Combined	   1.5888282	0.020477538	0.188	0.188	
Noise vs Combined	   7.6738300	0.087527031	0.001	0.001	**	





######################
## we can also use nonmetric multidimensional scaling to visualize differences between sites  
####### testing plotting metaMDS


```{r}
# scree plot 

scree<-nmds(betaD,mindim=1, maxdim=5, nit=10)
stress<-scree$stress
plot(stress)

axis.seq<-c(seq(1,1, length=10), seq(2,2,length=10), seq(3,3, length=10), seq(4,4,length=10), seq(5,5,length=10))
plot(stress~factor(axis.seq))
```

# run an MDS on the data
# FIRST MAKE A DISTANCE MATRIX USING a distance matrix THEN SEND TO NMDS

```{r, include=FALSE}
D3.mds<-metaMDS(betaD, k=3, trymax=200)
D3.mds 
```


```{r}
#### display three versions with each showing proportion of guild of total
## see if 3D NMDS will be better to display
plot(D3.mds, las=1) ## open circles are points and crosses are species

Env <- data.frame(d$Treatment)
fit <- envfit(D3.mds, Env)
fit
plot(fit)
```


```{r}
par(mfrow=c(1,2))

# axes 1 and 2
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,2))

ordihull(D3.mds,groups=d$Treatment,draw="polygon",col=c("grey44", "pink", "skyblue", "red"),label=F)
points(D3.mds, display = "sites", pch = 21, cex = 2)

# axes 1 and 3
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,3), xlab ="NMDS1", ylab="NMDS3")
ordihull(D3.mds,groups=d$Treatment,draw="polygon",col=c("grey44", "pink", "skyblue", "red"),choices = c(1,3), label=F)
points(D3.mds, choices = c(1,3), display = "sites", pch = 21, cex = 2)
```


```{r}
##### now with oridispider
#ordispider(ord, groups, display="sites", w = weights(ord, display),
#  spiders = c("centroid", "median"),  show.groups, 
# label = FALSE, col = NULL, lty = NULL, lwd = NULL)

par(mfrow=c(1,2))

# axes 1 and 2
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,2))
ordispider(D3.mds,groups=d$Treatment,display="sites",col=c("grey44", "pink", "skyblue","red"),label=F, lwd=3, choices = c(1,2))
points(D3.mds, display = "sites", pch = 21, cex = 0.25, choices = c(1,2))

# axes 1 and 3
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,3), xlab ="NMDS1", ylab="NMDS3")
ordispider(D3.mds,groups=d$Treatment,display="sites",col=c("grey44", "pink", "skyblue", "red"),label=F, lwd=3, choices = c(1,3))
points(D3.mds, display = "sites", pch = 21, cex = 0.25, choices = c(1,3))
```


