---
title: "Untitled"
author: "JWILLEMS"
date: "3/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, include=FALSE}
library(vegan)
library(multcomp)
library(lme4)
library(performance)
library(MuMIn)
library(blmeco)
library(matrixStats)
library(ecodist)
library(MASS)
options(na.action = "na.fail")
```


```{r}
d <- read.csv("CamTaxaBinary2.csv", header=TRUE)
head(d)
```

```{r}
names(d)
dd <- as.matrix(d[2:9])

d$detect <- ifelse(d$rich < 1, 0, 1)
```


```{r}
## how many zeros per treatment
d_zero <- subset(d, d$rich < 1)     ## No zeros 
d_zero
```


```{r}
# The following indices have binary versions
# use which ever maximizes index. Try gradients of light and noise, but also treatment categories

rankindex(d$M_Illum, d[2:9],indices = c("euclidean", "manhattan", "gower", "altGower", "canberra", "clark", "kulczynski", "horn", "binomial", "jaccard", "bray"))

# for lux, kulczynski
# for laeq, kulczynski, gower, manhattan, euclidean, binomial
# for treatment, kulczynski, altGower, canberra, clark, horn
# for moon phase: kulczynski, clark, canberra

betaD <-vegdist(d[2:9], method ="kulczynski", binary=TRUE)

```


```{r}
#### we can now use a permanova to see whether we see turnover among our treatments

adonis(betaD ~ d$Treatment + d$Laeq + d$Lux + d$M_Illum + d$Landcover + d$JDay + d$Treatment*d$M_Illum + d$Lux*d$M_Illum + d$Lux*d$Laeq)  #kulczynski binary method

### add pair.wise adonis for treatment conparisons

pairwise.adonis(x=d[,2:9], factor = d$Treatment, sim.function="vegdist", sim.method = "kulczynski", p.adjust.m = "none")
```

Terms added sequentially (first to last)

             Df SumsOfSqs MeanSqs F.Model      R2 Pr(>F)  
d$Treatment   3     1.723 0.57426 2.76622 0.04823  0.018 *
d$Laeq        1     0.056 0.05572 0.26839 0.00156  0.755  
d$Lux         1     0.517 0.51735 2.49209 0.01448  0.093 .
Residuals   161    33.423 0.20760         0.93572         
Total       166    35.719                 1.00000   


      Pair             F.Model      R2        p    pADJ
Control vs Light	    0.8930888	0.01064556	0.417	0.417	
Control vs Noise	    3.3208440	0.03676719	0.027	0.027	*
Control vs Combined  	0.8736372	0.01067056	0.467	0.467	
Light vs Noise	      4.3037238	0.04986719	0.020	0.020	*
Light vs Combined	    1.7464755	0.02246373	0.158	0.158	
Noise vs Combined	    6.6180177	0.07640463	0.004	0.004	*








######################
## we can also use nonmetric multidimensional scaling to visualize differences between sites  
####### testing plotting metaMDS


```{r}
# generate a scree plot to determine the parsimonious axis number

scree<-nmds(betaD,mindim=1, maxdim=5, nit=10)
stress<-scree$stress
plot(stress)

axis.seq<-c(seq(1,1, length=10), seq(2,2,length=10), seq(3,3, length=10), seq(4,4,length=10), seq(5,5,length=10))
plot(stress~factor(axis.seq))


###A good rule of thumb: stress > 0.05 provides an excellent representation in reduced dimensions, > 0.1 is great, >0.2 is good/ok, and stress > 0.3 provides a poor representation.**
# https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/
```

# run an MDS on the data
#####FIRST MAKE A DISTANCE MATRIX USING a distance matrix THEN SEND TO NMDS

```{r, include=FALSE}
D3.mds<-metaMDS(betaD, k=3, trymax=100)
D3.mds ### 
```


```{r}
#### display three versions with each showing proportion of guild of total
## see if 3D NMDS will be better to display
plot(D3.mds, las=1) ## open circles are points and crosses are species

Env <- data.frame(d$Treatment)
fit <- envfit(D3.mds, Env)
fit
plot(fit)
```


```{r}
par(mfrow=c(1,2))

# axes 1 and 2
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,2))

ordihull(D3.mds,groups=d$Treatment,draw="polygon",col=c("grey44", "pink", "skyblue", "red"),label=F)
points(D3.mds, display = "sites", pch = 21, cex = 2)

# axes 1 and 3
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,3), xlab ="NMDS1", ylab="NMDS3")
ordihull(D3.mds,groups=d$Treatment,draw="polygon",col=c("grey44", "pink", "skyblue", "red"),choices = c(1,3), label=F)
points(D3.mds, choices = c(1,3), display = "sites", pch = 21, cex = 2)
```


```{r}
##### now with oridispider
#ordispider(ord, groups, display="sites", w = weights(ord, display),
#  spiders = c("centroid", "median"),  show.groups, 
# label = FALSE, col = NULL, lty = NULL, lwd = NULL)

par(mfrow=c(1,2))

# axes 1 and 2
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,2))
ordispider(D3.mds,groups=d$Treatment,display="sites",col=c("grey44", "pink", "skyblue","red"),label=F, lwd=3, choices = c(1,2))
points(D3.mds, display = "sites", pch = 21, cex = 0.25, choices = c(1,2))

# axes 1 and 3
plot(D3.mds, type = "n", las=1,  xlim=c(-0.5,0.5), ylim=c(-0.5,0.5), choices = c(1,3), xlab ="NMDS1", ylab="NMDS3")
ordispider(D3.mds,groups=d$Treatment,display="sites",col=c("grey44", "pink", "skyblue", "red"),label=F, lwd=3, choices = c(1,3))
points(D3.mds, display = "sites", pch = 21, cex = 0.25, choices = c(1,3))
```



























