---
title: "SiteSppBinary_Adonis2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, include=FALSE}
library(tidyverse)
library(vegan)
library(vegan3d)
library(multcomp)
library(lme4)
library(performance)
library(MuMIn)
library(blmeco)
library(matrixStats)
library(ecodist)
library(MASS)
library(rgl)
library(ggeffects)
library(patchwork)
options(na.action = "na.fail")
```


```{r}
d <- read.csv("Data/CamSppBin2.csv", header=TRUE)
head(d)
```

```{r}
# how many zeros per treatment
d_zero <- subset(d, d$rich < 1)     # Very few zeroes now, only 4 cameras
d_zero

# cameras with zero detections cannot be included
d2 <- subset(d, d$rich > 0)

# how many non zero cameras are left per treatment?
sapply(split(d2$Treatment, d2$Treatment), length) # slightly fewer cameras at combined and light treatments
```


```{r}
rankindex(d2$Lux, d2[2:24],indices = c("euclidean", "manhattan", "gower", "altGower", "canberra", "clark", "kulczynski", "horn", "binomial", "jaccard", "bray"))

# for lux: euclidean, manhattan, gower, binomial, altGower, canberra
# for laeq: kulczynski, altGower, canberra, clark, horn, jaccard, bray
# for treatment: euclidean, manhattan, gower, binomial, jaccard


betaD1 <-vegdist(d2[2:24], method ="gower", binary=TRUE) # for Treatment model

betaD2 <-vegdist(d2[2:24], method ="altGower", binary=TRUE) # for Lux/LAeq model
```


From blog post: https://mcfromnz.wordpress.com/2011/03/02/anova-type-iiiiii-ss-explained/

Type III:

SS(A | B, AB) for factor A.
SS(B | A, AB) for factor B.

This type tests for the presence of a main effect after the other main effect and interaction. This approach is therefore valid in the presence of significant interactions.

However, it is often not interesting to interpret a main effect if interactions are present (generally speaking, if a significant interaction is present, the main effects should not be further analyzed).

If the interactions are not significant, type II gives a more powerful test.

```{r}
adonis2(betaD2 ~ Lux*Laeq +
                Lux + 
                Laeq +
                mIndex + 
                Landcover + 
                JDay, 
                strata = d2$Cluster, 
                by = "margin", data = d2) 


adonis2(betaD2 ~ Lux + 
                Laeq +
                mIndex + 
                Landcover + 
                JDay, 
                strata = d2$Cluster, 
                by = "margin", data = d2) 


adonis2(betaD1 ~ Treatment +
                mIndex + 
                Landcover + 
                JDay, 
                strata = d2$Cluster, 
                by = "margin", data = d2) 
```

Model: Lux*LAeq

#           Df SumOfSqs   R2      F    Pr(>F)   
Lux:Laeq    1    0.435 0.01013 1.6723  0.131 
mIndex      1    1.022 0.02377 3.9228  0.005 **
Landcover   1    0.263 0.00612 1.0095  0.365   
JDay        1    0.235 0.00546 0.9006  0.484   
Residual  152   39.581 0.92109                 
Total     158   42.972 1.00000    

---------------------------------------------------

Model: Lux + LAeq

#           Df SumOfSqs      R2      F Pr(>F)   
Lux         1    0.446 0.01038 1.7059  0.116   
Laeq        1    0.174 0.00405 0.6651  0.716   
mIndex      1    1.045 0.02432 3.9954  0.004 **
Landcover   1    0.248 0.00576 0.9463  0.410   
JDay        1    0.234 0.00545 0.8961  0.501   
Residual  153   40.016 0.93123                 
Total     158   42.972 1.00000  

---------------------------------------------------

Model: Treatment

#           Df SumOfSqs      R2      F Pr(>F)   
Treatment   3  0.02264 0.03424 1.9046  0.050 *  
mIndex      1  0.02054 0.03106 5.1828  0.001 ***
Landcover   1  0.00150 0.00226 0.3779  0.771    
JDay        1  0.01052 0.01590 2.6541  0.039 *  
Residual  152  0.60239 0.91083                  
Total     158  0.66136 1.00000 




```{r, Treatment pairwise comparison}
pairwise.adonis(x=d2[,2:24], factor = d2$Treatment, sim.function="vegdist", sim.method = "gower", p.adjust.m = "none")
```


Comparison                F.Model   R2          p.value
Control vs Light	        1.295382	0.01593427	0.297		
Control vs Noise	        2.762674	0.03184173	0.051	.	
Control vs Combined	      1.441255	0.01837368	0.255		
Light vs Noise	          1.901872	0.02380260	0.123	.	
Light vs Combined	        2.870963	0.03886456	0.031 *
Noise vs Combined	        1.684631	0.02196830	0.174		



## FIGURES



```{r}
leqD <- dist(d2$Laeq)
luxD <- dist(d2$Lux)
mIndexD <- dist(d2$mIndex)
JDayD <- dist(d2$JDay)
betaDv <- c(betaD2) 

envD <- data.frame(c(leqD),c(luxD),c(JDayD), c(mIndexD), betaDv)
names(envD) <- c("LeqD", "LuxD", "JDayD", "MoonIndexD", "betaDdf")

betaDMod <- lm(betaDdf ~ LeqD* LuxD + JDayD + MoonIndexD, data = envD)

summary(betaDMod)
```

```{r}
DFsdB <- ggpredict(betaDMod, terms = c("LeqD", "LuxD"), back.transform =F, type ="fe")

C1 <- plot(DFsdB, colors="eight", add.data=F)  + 
      labs(x="Sound difference (dB)", y ="Dissimilarity", title ="") + 
      theme_classic(base_size = 36) + 
      theme(panel.grid.minor = element_blank()) + 
      theme(axis.line = element_line(colour = "black")) +
      theme(legend.position = "none") +
      labs(subtitle = "(a)") +
      theme(plot.subtitle = element_text(size = 36, face = "bold")) +
      theme(plot.subtitle = element_text(hjust = -0.13))
C1
```

```{r}
DFsLux <- ggpredict(betaDMod, terms = c("LuxD", "LeqD"), back.transform =F, type ="fe")

D1 <- plot(DFsLux, colors="eight", add.data=F)  + 
      labs(x="Light difference (Lux)", y ="Dissimilarity", title ="") + 
      theme_classic(base_size = 36) + 
      theme(panel.grid.minor = element_blank()) + 
      theme(axis.line = element_line(colour = "black")) +
      theme(legend.position = "none") +
      labs(subtitle = "(b)") +
      theme(plot.subtitle = element_text(size = 36, face = "bold")) +
      theme(plot.subtitle = element_text(hjust = -0.13))
      
D1
```

```{r}
DFsMoon <- ggpredict(betaDMod, terms = c("MoonIndexD", "LeqD"), back.transform =F, type ="fe")

M1 <- plot(DFsMoon, colors="eight", add.data=F)  + 
      labs(x="Moonlight difference", y ="Dissimilarity", title ="") + 
      theme_classic(base_size = 36) + 
      theme(panel.grid.minor = element_blank()) + 
      theme(axis.line = element_line(colour = "black")) +
      theme(legend.position = "none") +
      labs(subtitle = "(c)") +
      theme(plot.subtitle = element_text(size = 36, face = "bold")) +
      theme(plot.subtitle = element_text(hjust = -0.13))
M1
```

```{r}
C1 / D1 / M1
```




## Indicator Species Analysis


```{r}
library(indicspecies)

indSpp <- multipatt(d2[2:24], d2$Treatment, control = how(nperm=999))

summary(indSpp)
```

Combined Treatment 
        stat   p.value    
Turkey 0.378   0.001 ***

-------------------------

Light Treatment 
           stat   p.value  
Scrub.Jay 0.328   0.011 *

-------------------------

Group Noise Treatment 
          stat   p.value  
Grey.fox 0.273   0.043 *





```{r}
datGrouped <- d2 %>% dplyr::select(3:24, 27)

datGrouped <- datGrouped %>% 
   pivot_longer(!Treatment, names_to = "Taxa", values_to = "count") %>% 
   group_by(Treatment, Taxa) %>% 
   summarise(Count = sum(count))
```

```{r}
p1 <- datGrouped %>% 
   ggplot(aes(fill = Taxa, x = Treatment, y = Count)) + 
   geom_bar(position="stack", stat="identity") + 
   labs(y="# Cameras Detected At") +
   facet_wrap(~Taxa) + 
   theme_bw(base_size = 18) +
   theme(legend.position = "none") 

p1
```















